% !TeX spellcheck = en_GB
%-------------------------
% CV in LaTeX
% Author: Jean Lucien Randrianantenaina
% License: MIT
%------------------------
\documentclass[a4paper,oneside]{article}

% Encoding and Font Packages
\usepackage[utf8]{inputenc}
\usepackage{cmap}
\usepackage[default]{lato}
\usepackage{accsupp}

% Mathematics Packages
\usepackage{amsmath,amsfonts,amssymb}

% Graphics and Layout Packages
\usepackage{graphicx}
\usepackage[left=10mm,right=10mm,top=10mm,bottom=10mm]{geometry}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage[explicit]{titlesec}
\usepackage{tikz}

% Text and List Formatting Packages
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{ragged2e}

% Header and Hyperlink Packages
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}

% Additional Utility Packages
\usepackage{etoolbox}
\usepackage{calc}
\usepackage{xparse}
\usepackage{ifthen}
\usepackage{fontawesome5}

% Document Settings
\pagestyle{empty}
\parindent=0pt

% Color Definitions
\definecolor{DefaultBlack}{HTML}{222222}
\definecolor{DarkGreen}{HTML}{0370AA}
\definecolor{LightBlack}{HTML}{333333}
\definecolor{LightGray}{HTML}{666666}
\definecolor{LinkColor}{HTML}{005877}

\colorlet{default}{DefaultBlack}
\colorlet{heading}{DarkGreen}
\colorlet{headingrule}{DarkGreen}
\colorlet{emphasis}{LightBlack}
\colorlet{body}{LightGray}
\colorlet{link}{LinkColor}

% Utility Commands
\newlength{\lfonts}
\setlength{\lfonts}{\the\fontdimen5\font}
\NewDocumentCommand{\link}{m}{\color{link}\underline{#1}}

% Section Formatting
\titleformat{\section}
{\fontsize{11}{10}\selectfont\bfseries}
{}
{0pt}
{\textcolor{heading}{#1}}
[\vspace*{-1.5\lfonts}\textcolor{headingrule}{\rule{\linewidth}{1.5pt}}\vspace*{-\lfonts}]

% Custom CV Commands
\NewDocumentCommand{\cvName}{m}{\parbox{\linewidth}{\Large\bfseries #1}\par\vspace*{5pt}}
\NewDocumentCommand{\cvTitle}{m}{\makebox[0.5\linewidth][l]{\large\bfseries #1}}
\NewDocumentCommand{\cvLink}{mm}{\href{#2}{#1\ \color{link}\faExternalLink*}}
\NewDocumentCommand{\cvProjectTitle}{mm}{\href{#2}{\textbf{#1}~\color{link}\faExternalLink*}}

% Personal Info Commands
\NewDocumentCommand{\cvAddress}{m}{\color{heading}\faHome\ \color{emphasis}#1}
\NewDocumentCommand{\cvPhone}{m}{\color{heading}\faPhone\ \color{emphasis}#1}
\NewDocumentCommand{\cvMail}{m}{\color{heading}\faAt\ \color{emphasis}#1}
\NewDocumentCommand{\cvWebsite}{m}{\color{heading}\faGlobe\ \color{emphasis}#1}
\NewDocumentCommand{\cvLinkedIn}{m}{\color{heading}\faLinkedin\ \color{emphasis}#1}
\NewDocumentCommand{\cvGitHub}{m}{\color{heading}\faGithub\ \color{emphasis}#1}

\NewDocumentCommand{\cvtag}{m}{\tikz[baseline]\node[anchor=base,draw=gray!30,rounded corners,inner xsep=1ex,inner ysep=0.75ex,text height=1.5ex,text depth=.25ex]{#1};}


\NewDocumentCommand{\cvEntry}{mmmm}{\parbox{\linewidth}{
		\begin{tabular}{@{}>{\raggedleft\arraybackslash}p{3cm}p{\linewidth - 3.5cm}@{}}
			{#1} & \textbf{#2}  \\
			\ifstrempty{#3}{}{&#3\\}
			\ifstrempty{#4}{}{&#4}
		\end{tabular}%
	}\par\vspace*{5pt}}


\begin{document}
	\fontsize{9}{12}\selectfont
\begin{minipage}{\linewidth}
		\cvName{Jean Lucien Randrianantenaina}
		\begin{tabbing}
			\hspace{7cm}\=\kill
			\cvAddress{Beravina, Fianarantsoa, Madagascar} \>
			\href{https://www.linkedin.com/in/jean-lucien-randrianantenaina-82b98622b}{\cvLinkedIn{\link{Jean Lucien Randrianantenaina}}} \\[2pt]
			\href{mailto:rjlucienaina@gmail.com}{\cvMail{\link{rjlucienaina@gmail.com}}} \>
			\href{https://fahazavana.github.io}{\cvWebsite{\link{fahazavana.github.io}}} \\[2pt]
			\href{tel:+261345898164}{\cvPhone{+261 34 58 981 64}} \>
			\href{https://github.com/Fahazavana}{\cvGitHub{\link{Fahazavana}}} \\[2pt]
		\end{tabbing}
	\end{minipage}

	\section{Experience}
	\cvEntry{Jan. 2025 -- Present}{ML/AI \& Back-end Developer}{Arato, Fianarantsoa, Madagascar}
	{\vspace*{-3.5ex}\begin{itemize}[itemsep=-1ex, leftmargin=0.3cm]
			\item AI/ML Development: Designed and deployed AI models (RAG, chatbots); built recommendation and NLP solutions; fine-tuned models for optimal performance.
			\item Built data scraping pipelines (Selenium); automated workflows (n8n); streamlined processes to minimise manual work.
			\item Back-end Services: Developed scalable back-end systems; designed RESTful APIs; ensured secure and efficient data management.
	\end{itemize}}
	\vspace*{-2ex}
	\cvEntry{Jan. 2025 -- Present}
	{Part-time Lecturer}
	{University of Fianarantsoa, Madagascar}
	{\vspace*{-3.5ex}\begin{itemize}[itemsep=-1ex, leftmargin=0.3cm]
			\item Delivered lectures in Linear Algebra and Mathematics for Artificial Intelligence.
			\item Developed course materials and supervised student projects, assignments, and examinations.
		\end{itemize}
	}
	\vspace*{-3ex}

	\section{Education}
	\cvEntry{01/2024 -- 12/2024}
	{MSc in Machine Learning and Artificial Intelligence}
	{Stellenbosch University, South Africa}
	{Grade: 78/100}
	\cvEntry{06/2019 -- 01/2024}
	{MSc in Mathematics and Applications -- Fundamental Mathematics}
	{University of Fianarantsoa, Madagascar}
	{Grade: 14.25/20}
	\cvEntry{09/2022 -- 06/2023}
	{MSc in Mathematical Sciences -- Fundamental Sciences}
	{African Institute for Mathematical Sciences (AIMS), Cameroon}
	{CGPA: 3.52/4}
	\cvEntry{11/2015 -- 04/2019}
	{BSc in Mathematics and Applications -- Fundamental Mathematics}
	{University of Fianarantsoa, Madagascar}
	{Grade: 14.69/20}

	\section{Research Projects}
	\cvEntry{2024}
	{\cvProjectTitle{Conditional Flow Matching (CFM) in Feature Space (MSc Project)}{https://drive.google.com/file/d/1-L48H03LKxXeq2_slVyiwi7375ldzKQT/view?usp=sharing}}
	{}{\textbf{Supervisors:} Dr Shane Josias and Prof. Willie Brink}
	\cvEntry{2024}
	{Optimization of the UNet Architecture for Brain Tumour Segmentation with Genetic Algorithm (MSc Project)}{}
	{\textbf{Supervisors:} Dr Aurelle Tchagna Kuanou and Dr Joelson Randriamparany}
	\cvEntry{2023}
	{\cvProjectTitle{Carmichael Number (MSc Project)}{https://drive.google.com/file/d/1ZsKUTz0doOZWS44VHkibO2A6zSbmKSce/view?usp=sharing}}
	{}{\textbf{Supervisor:} Prof. Florian Luca}
	\cvEntry{2019}
	{\cvProjectTitle{Radical Resolution of Polynomial Equation (BSc Project)}{https://drive.google.com/file/d/1i-suhMOuUgvXlcELPMTabQIKtV5L7l2R/view?usp=sharing}}
	{}{\textbf{Supervisor:} Prof. Solo Rajaofetra Randriamahaleo}

	\section{Certifications}
	\cvEntry{07/2023}
	{Business Management}
	{ESMT Berlin, II Africa, IIP -- Limbé, Cameroon}
	{One-month intensive course in business management and soft skills development.}
	\cvEntry{01/2022 -- 07/2022}
	{Back-end Developer}
	{SAYNA \& OIF: DCLIC Programme 1.0 -- Fianarantsoa, Madagascar}
	{Six months of training in website development: HTML5, CSS3, JavaScript, Node.js, MySQL.}

	\section{Publications and Talks}
	\cvEntry{Publication}
	{There Is No Carmichael Number of the Form $2^np^2+1$ with $p$ Prime}
	{Florian Luca and Jean Lucien Randrianantenaina, \cvLink{INTEGER, Volume 23 (2023)}{http://math.colgate.edu/~integers/x51/x51.pdf}}
	{}
	\cvEntry{Talk}
	{Fermat's Last Theorem, with $n=4$}
	{Presented to AIMS Cameroon Students}
	{}

	\section{Awards and Scholarships}
	\cvEntry{2024}
	{Google DeepMind Scholarship}
	{Fully funded Master's Programme in Machine Learning and Artificial Intelligence at Stellenbosch University}
	{}
	\cvEntry{2023}
	{Industry Immersion Programme (IIP) Scholarship}
	{Fully funded programme on business management, offered by AIMS, II Africa, ESMT Berlin, Germany}
	{}
	\cvEntry{2022}
	{MasterCard Foundation Scholarship}
	{Fully funded Master's Programme at AIMS Cameroon}
	{}
	\cvEntry{2022}
	{D-CLIC Programme}
	{Programme funded by the Organisation Internationale de la Francophonie (OIF) and SAYNA}
	{}

	\section{Projects}
	\cvEntry{07/2024}
	{\cvProjectTitle{Reinforcement Learning}{https://github.com/Fahazavana/Reinforcement_Learning}}
	{Implemented Q-Learning, SARSA, and two variants of Deep Q-Network algorithms to solve the mini-grid problem using Gymnasium and PyTorch.}
	{}
	\cvEntry{07/2024}
	{\cvProjectTitle{Neural Machine Translation}{https://github.com/Fahazavana/Neural_Machine_Translation}}
	{Developed a neural machine translation model and further trained an existing pre-trained model (opus-mt-en-af) to translate engineering assessments from English to Afrikaans.}
	{}
	\cvEntry{06/2024}
	{\cvProjectTitle{Byte Pair Encoding (BPE) and Trigram Language Model}{https://github.com/Fahazavana/NGramLMs_BPE}}
	{Implemented a trigram language model for language identification and Byte-Pair Encoding (BPE) for language similarity analysis.}
	{}
	\cvEntry{02/2024}
	{Movie Recommender System}
	{Built a large-scale recommender system using probabilistic matrix factorisation, trained on the 25M MovieLens dataset. Implemented from scratch using Python, Numba, and NumPy.}
	{}
	\cvEntry{2023}
	{\cvProjectTitle{MK-Forum}{https://github.com/Fahazavana/MK-Forum}}
	{Developed a web forum dedicated to mathematics. Built the front-end using HTML, CSS/Bootstrap, and JavaScript. The back-end uses Python/Django and MySQL. Includes features like user accounts, posts, comments, and a voting system.}
	{}
	\cvEntry{2022}
	{\cvProjectTitle{Unbeatable TicTacToe}{https://github.com/Fahazavana/SAYNA-JAVASCRIPT-MORPION-042022}}
	{Developed a Tic-Tac-Toe game using HTML, CSS, and JavaScript. Features an unbeatable computer opponent using a combination of random placement and a min-max algorithm based on difficulty level.}
	{}
	%	\cvEntry{2022}
	%	{\cvProjectTitle{Pendu Malagasy}{https://github.com/Fahazavana/Pendu_Malagasy}}
	%	{Created a hangman game with Python/Tkinter. The word list defaults to Malagasy but can be changed easily.}
	%	{}
	\cvEntry{2021}
	{\cvProjectTitle{Bellman-Kalaba GUI}{https://github.com/Fahazavana/Bellman-Kalaba}}
	{Developed a graphical user interface for graph representation and short-path finding using the Bellman-Kalaba algorithm with Tkinter/Python.}
	{}

	\section{Skills}
	\cvEntry{Language Skills}{Malagasy (Native), French (Fluent), English (Upper-Intermediate)}{}{}
	\cvEntry{Programming Languages}{Python, JavaScript}{}{}
	\cvEntry{Frameworks, Libraries, Runtimes}{PyTorch, TensorFlow, JAX, Pandas, Scikit-Learn, Langchain, Django, Flask, FastAPI, Bootstrap, Node.js, Vue.js}{}{}
	\cvEntry{Database}{MySQL, PostgreSQL, Chroma, MongoDB}{}{}
	\cvEntry{Version Control}{Git}{}{}
	\cvEntry{Other Skills}{\LaTeX, HTML, CSS/SASS, MS Office}{}{}
%	\section{References}
%	\hspace*{15pt}Available upon request

	\vfill
	{\color{body}Jean Lucien Randrianantenaina \hfill \href{mailto:rjlucienaina@gmail.com}{rjlucienaina@gmail.com}}
\end{document}